---
title: "Bioinformatic analysis"
author: "Rodrigo Aguilar"
date: "2023-10-05"
output: pdf_document
---

Woman affected by a rare disease, she has one brother and a sister healthy; their parents also are healthy.

```{r}
setwd("~/Downloads/Claudia")

F10 <- read.csv("FAM10.csv", sep = ",", header = T)

# 22679 variants with 52 variants.
```

## Data:

- TR: coverage greater than 10

- GQ: Quality greater than 30

- RATIO: Alellic balance grater than 0.20

- ANNOTATION: no synonymous SNV

- EVE_ALT_FREQ: frequency less than 0.01

```{r}
F10_s <- subset(F10, TR >= 10 & GQ >= 30 & RATIO >= 0.20 & ANNOTATION != "synonymous SNV" &  EVE_ALT_FREQ <= 0.01)
```



### Filtering:

### 1. Recesive disease

If it is a recesive trait then, the patient is homozygous, both parents are heterozygous, and the brothers can have any genotype but no homozygous

```{r}
hz <- subset(F10_s, Proband.ZYG == "Proband:hom" & Mother.ZYG == "Mother:het" & Father.ZYG == "Father:het" & UASib.ZYG != "UASib:hom" & UASib.ZYG.1 != "UASib:hom") 
```

List of candidates:

```{r}
hz
```